On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-18 article/ms.tex
proof read

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 10,000 r-process enhanced stars in the Milky Way, \todo{and about $0.087$ in LAMOST DR2}. We find that neutron star mergers are able to create all currently known r-process enhanced stars within \todo{X} years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

	\begin{keywords}
		nucleosynthesis -- r-process -- neutron star mergers -- core-collapse supernovae
	\end{keywords}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
	Rapid neutron capture occurs when the neutron density is high enough such that the rate of neutron capture will occur faster than the rate at which an isotope undergoes a $\beta$-decay. Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}. Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material. Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of significant contribution by r-process material. Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a core-collapse supernovae event.
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.

	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either. Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material. One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way? On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process star? If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.

@@

	\subsection{Multiple r-process sites?}
	While it is possible that all known r-process enhanced stars could be made by neutron star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$). These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.

	\subsection{Core-collapse supernovae}
	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}. Currently, the exact  mechanism that allows material with a high enough neutron density in order to produce  r-process material is unknown.
%	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse. In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions. However, how much enhanced material is released from the event depends heavily on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.

@@

	\subsection{Neutron star mergers}
	\label{NSmerg}
	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}. However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}. The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.

	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case of a single r-process site. Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron star merger. However, two of the stars observed were only weakly enhanced in r-process elements which suggests that there must have been a second, less efficient, form of r-process enhancement present.

	\subsection{The rates of r-process events and what they imply}
	\label{rates}
	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in Section \ref{NSmerg}. Reliable estimates of core-collapse supernovae are also available \citep{Li2011}. From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron star mergers, or purely by core-collapse supernovae. As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way. We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.

	\todo{1. Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age  of  universe. 2. Calculate  mass of Eu in each 0.8 solar mass star. 3. How many we expect in that 15 kpc sphere throughout universe? 4. Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc. 5. Repeat for CCSN. 6. Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}
	In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3\,stars per year. We considered a spherical volume out to $r_\textrm{GC} = 15\,{\rm kpc}$ from the  centre of the Galaxy. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the percentage of the Milky Ways stars that our sample of r-process  stars represents.

	We assume that a star is said to be enhanced if $[{\rm Eu/Fe}] \geq 0.7$, and assert that all 47 stars here exhibit abundances exceeding this lower-bound. Taking the mass of europium ejected from a neutron star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, this allows us to calculate  a density of europium $\rho_{\rm Eu}$,
\begin{equation}
	\centering
	\rho_{\rm Eu} = M_\textrm{Eu}\frac{dN}{dt}(13.87\times10^9\,{\rm yr})
\end{equation}

\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$).

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{equation}
	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
	\end{equation}
	Where:
	\begin{equation}
	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\\
	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
	\end{equation}
	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$

    It was found that in the Milky Way there should be present 9,896 r-process stars enhanced solely from neutron star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.

    Scaling down from the 250 billion stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of enhanced stars we expect to find comes to less than one (0.0178). If we are to extend our sample from the 450000 giants, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should still have found less than a single star (0.087) enhanced in r-process elements. While again this should be considered a lower bound, it is nonetheless a startling difference from the 47 that were found.

    We can do a similar calculation with our rate of core-collapse supernovae. Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 442 r-process enhanced stars made solely from core-collapse supernovae.

    Were we to scale this down to our sample size of $\approx450000$ giants we arrive at a figure of $8.0\times10^{-4}$ stars that should have been observed. Scaling again to the full LAMOST sample we would then expect to find $3.9\times10^{-3}$ enhanced stars.

    From these estimates we can find an approximation for whether or not either neutron star mergers or core-collapse supernovae by themselves are sufficient to enrich our entire r-process enhanced catalogue.

    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^9$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, not at all within the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

    This is reinforced by our r-process enhanced stars found in the LAMOST sample. Our 47 stars represent greater then 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars. However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way. It is highly unlikely that 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.

    In an effort to confirm this, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to 9896 stars from the previous calculation.

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. These 47 stars represent the first r-process enhanced stars found at [Fe/H] $>-2$. The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky. We present the first estimate, to our knowledge, that neutron star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe. We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $80$ in LAMOST DR2. We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

	\begin{keywords}
		nucleosynthesis -- r-process -- neutron-star mergers -- core-collapse supernovae
	\end{keywords}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
	Rapid neutron capture occurs when the neutron density is high enough such that the rate of neutron capture will occur faster than the rate at which an isotope undergoes a $\beta$-decay. Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}. Sites meeting this criteria include core-collapse supernovae, neutron-star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material. Neutron-star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
	Magnetorotationally driven supernovae may not produce as much r-process material as neutron-star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron-star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of significant contribution by r-process material. Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a core-collapse supernovae event.
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron-star merger.

	While neutron-star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either. Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material. One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way? On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process star? If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.

@@

	\subsection{Multiple r-process sites?}
	While it is possible that all known r-process enhanced stars could be made by neutron-star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$). These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.

	\subsection{Core-collapse supernovae}
	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}. Currently, the exact  mechanism that allows material with a high enough neutron density in order to produce  r-process material is unknown.
%	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron-star during core-collapse. In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions. However, how much enhanced material is released from the event depends heavily on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.

@@

	\subsection{Neutron-star mergers}
	\label{NSmerg}
	Neutron-star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}. However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}. The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.

	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case of a single r-process site. Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron-star merger. However, two of the stars observed were only weakly enhanced in r-process elements which suggests that there must have been a second, less efficient, form of r-process enhancement present.

	\subsection{The rates of r-process events and what they imply}
	\label{rates}
	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron-star mergers occur, as mentioned in Section \ref{NSmerg}. Reliable estimates of core-collapse supernovae are also available \citep{Li2011}. From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron-star mergers, or purely by core-collapse supernovae. As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way. We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms. In these calculations a star is deemed to be 'enhanced' where $[{\rm Eu/Fe}] \geq 0.7$.

	\todo{1. Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age of universe. DONE 2. Calculate  mass of Eu in each 0.8 solar mass star DONE. 3. How many we expect in that 15 kpc sphere throughout universe? 4. Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc. 5. Repeat for CCSN. 6. Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}

	Taking the mass of europium ejected from a neutron-star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, we can calculate a density of Europium $\rho_{\rm Eu}$,
\begin{equation}
	\centering
	\rho_{\rm Eu} = M_\textrm{Eu}\frac{dN}{dt}(13.87\times10^9\,{\rm yr})
\end{equation}

\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron-star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$). From this calculation we expect there to be present $\approx1.23 \times 10^{25}$ kilograms of Europium within a 15 kpc radius sphere from the centre of the Milky Way.

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{equation}
	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
	\end{equation}
	Where:
	\begin{equation}
	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\
	\end{equation}
	\begin{equation}
	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
	\end{equation}
	The number of Hydrogen atoms was approximated from the Hydrogen atomic mass, and the assumption was made that a giant star will be composed of $\approx$75\% Hydrogen and each star possesses an average mass of $\approx 0.8\ M_{\odot}$. These assumption mean that a Europium mass of $9.3 \times 10^{20}$ kilograms is required to be present in the star for it to be deemed 'enhanced'.

    It was found that in the Milky Way there should be present 13,194 r-process stars enhanced solely from neutron-star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.

    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents. Multiplying this fraction by the 13,194 stars that should be present in the Milky Way, we expect to be present 80 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.

    %Scaling down from the 250 billion stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of enhanced stars we expect to find comes to less than one (0.0178). If we are to extend our sample from the 450000 giants, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should still have found less than a single star (0.087) enhanced in r-process elements. While again this should be considered a lower bound, it is nonetheless a startling difference from the 47 that were found.

    We can do a similar calculation with our rate of core-collapse supernovae. Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 590 r-process enhanced stars made solely from core-collapse supernovae. Applying the same method as utilised in the neutron-star merger calculations, we expect there to be present only 4 r-process enhanced stars in LAMOST DR2 enhanced entirely by core-collapse supernovae.

    %Were we to scale this down to our sample size of $\approx450000$ giants we arrive at a figure of $8.0\times10^{-4}$ stars that should have been observed. Scaling again to the full LAMOST sample we would then expect to find $3.9\times10^{-3}$ enhanced stars.

    From these estimates we find an approximation for whether or not either neutron-star mergers or core-collapse supernovae by themselves are sufficient to enrich our entire r-process enhanced catalogue.

    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^{9}$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

    This is reinforced by the r-process enhanced stars found in the LAMOST sample. Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars. However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way. It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.

    In an effort to confirm these numbers, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,194 stars from the previous calculation.

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. These 47 stars represent the first r-process enhanced stars found at [Fe/H] $>-2$. The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky. We present the first estimate, to our knowledge, that neutron-star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe. We also provide evidence to confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
